Analysis

### 2020-02-20 reports/DRM_exp/analysis_DRM_exp1.Rmd
new changes after revision from JL
new changes after revision
distances to targets

df <- readRDS(here("data", "exp_DRM1", "results_190509.rds"))

@@

@@

@@

```{r}

>>>>

df <- readRDS(here("data", "exp_DRM1", "results_191017.rds"))

@@

df2 <- readRDS(here("data/exp_DRM1/results_with_tgtdistances_200219.rds"))
```

@@

## New analysis based on review

### Distances from tgt images

```{r}
df2 <- df2 %>% 
  rowwise() %>% 
  mutate(mean_tgt_dist = unlist(dist_to_tgts) %>% mean(),
         min_tgt_dist = unlist(dist_to_tgts) %>% min())
df2 %>% 
  ggplot(aes(x = type, y = mean_tgt_dist)) + 
  stat_summary(fun.data = "mean_cl_boot", size = 1.5)

df2 %>% 
  ggplot(aes(x = type, y = min_tgt_dist)) + 
  stat_summary(fun.data = "mean_cl_boot", col = "red") + 
  geom_point(alpha = 0.1, position = position_jitter(0.2))

@@

```{r results accuracy}
